---
title: "Covid-19 Project"
author: "Deeksha Daga"
date: "May 5, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE }
library(gtools)
library(rjson)
library(plyr)
library(Metrics)
my.JSON <- fromJSON(file="https://pomber.github.io/covid19/timeseries.json")
India_json <- lapply(my.JSON$India, function(x){ unlist(x)})
India_df <- rbind.fill(lapply(India_json,function(x) do.call("data.frame", as.list(x))))
India_df <- do.call("rbind", India_json)
India_df <- as.data.frame(India_df)

cdate <- as.Date(India_df$date,format = "%Y-%m-%d")
cconfirmed <- as.numeric(India_df$confirmed)
cdeaths <- as.numeric(India_df$deaths)
crecovered <- as.numeric(India_df$recovered)

world_json <- lapply(my.JSON, function(x){unlist(x)})
world_df <- rbind.fill(lapply(world_json,function(x) do.call("data.frame",as.list(x))))
world_df <- do.call("rbind", world_json)
world_df <- as.data.frame(world_df)

wdate <- as.Date(world_df$date,format = "%Y-%m-%d")
wconfirmed <- as.numeric(world_df$confirmed)
wdeaths <- as.numeric(world_df$deaths)
wrecovered <- as.numeric(world_df$recovered)
#No. of days since 22-jan-2020
current = as.Date(Sys.Date())
start = as.Date("2020-01-22")
today = as.numeric(current - start)
options(scipen=999)

``` 


### Graph showing total confirmed cases in India:

```{r echo=FALSE}
# polynomial regression
cfit = lm(cconfirmed~poly(cdate,6))

#scatter plot
par(las=2,mgp=c(5,1,0),mar=c(6,6,6,6))
plot(cdate,cconfirmed,pch = 16,xlab = "date", col = "blue",xaxt = "n"
     ,ylab = "no. of cases ", main = "confirmed cases in india")
points(cdate,fitted(cfit),col="red",pch=1)
axis.Date(1, at=seq(min(cdate),max(cdate),by=10), format="%d %b %y")
legend("topleft",c("Actual","Predicted"), 
       col=c("blue","red"), lwd=2)
```

```{r echo=FALSE}
#prediction
a = today+1; b = today+7
new <- data.frame(cdate = as.Date(a:b ,origin = "2020-01-21"))
pred_confirmed <-predict.lm(cfit,new,interval = "confidence",level = 0.95)
newindia_df <- cbind(new, pred_confirmed)
names(newindia_df)[3] <- "minimum"
names(newindia_df)[4] <- "maximum"
names(newindia_df)[1] <- "date"
newindia_df$fit <- round(newindia_df$fit)
newindia_df$minimum <- round(newindia_df$minimum)
newindia_df$maximum <- round(newindia_df$maximum)
```

### Predictions for total confirmed cases in India for next week:

```{r echo=FALSE}
knitr::kable(newindia_df,align = "crrr",format.args = list(big.mark = ",", 
  scientific = FALSE))
```

```{r echo=FALSE}
errdate <- data.frame(date = as.Date(0:(today-101),origin = "2020-05-01"))
errfit <- predict.lm(lm(cconfirmed[101:today]~poly(cdate[101:today],6)),errdate)
errfit <- round(errfit)
actual <- cconfirmed[101:today]
#sse <- sum((errfit-actual)**2) # SSE
#rmse <- data.frame(rmse = sqrt(mean((err$errfit-err$actual)**2))) # RMSE
err <- cbind(errdate,errfit,actual)
#ae(actual,errfit)
err <- cbind(err,error = ape(actual,errfit)*100)
names(err)[2] <- "fit"
err$error <- round(err$error,2)
err$error <- paste(err$error,"%")
#rsq <- cor(err$fit, err$actual) ^ 2
```

### Graph showing total confirmed cases with our predictions for India:

```{r echo=FALSE}
par(las=2,mgp=c(5,1,0),mar=c(6,6,6,6))
plot(err$date,err$actual,pch = 16,xlab = "date", col = "blue",xaxt = "n"
     ,ylab = "no. of cases ", main = "confirmed cases in india")
points(err$date,err$fit,col="red",pch=1)
axis.Date(1, at=seq(min(err$date),max(err$date),by=1), format="%d %b %y")
legend("topleft",c("Actual","Predicted"), 
       col=c("blue","red"), lwd=2)
```

### Error Analysis:

```{r echo=FALSE}
knitr::kable(err,align = "crrr",format.args = list(big.mark = ",", 
  scientific = FALSE))
```

```{r echo=FALSE}
t_case=c();t_dead=c();t_recovered=c();t_date=c(1:today)
count=0
cols = seq(from=2, length=today,by=4)


for (j in cols){
  total_cases = 0
  total_deaths = 0
  total_recovered = 0
  count = count + 1
  for(i in world_df[,j]){
    total_cases = total_cases + as.numeric(i)
  }
  for(i in world_df[,j+1]){
    total_deaths = total_deaths + as.numeric(i)
  }
  for(i in world_df[,j+2]){
    total_recovered = total_recovered + as.numeric(i)
  }
  t_case[count] = as.numeric(total_cases)
  t_dead[count] = as.numeric(total_deaths)
  t_recovered[count] = as.numeric(total_recovered)
}
wdate <- as.Date(t_date,origin = "2020-01-21")
wdf = cbind(t_date,t_case,t_dead,t_recovered)

wdf <- as.data.frame(wdf)
wconfirmed <- as.numeric(wdf$t_case)
wdeaths <- as.numeric(wdf$t_dead)
wrecovered <- as.numeric(wdf$t_recovered)
```

### Graph showing total confirmed cases in World:

```{r echo=FALSE}
#polynomial regression
wfit = lm(wconfirmed~poly(wdate,6))

#scatter plot
par(las=2,mgp=c(5,1,0),mar=c(6,6,6,6))
plot(wdate,wconfirmed,pch = 16,xlab = "date", col = "blue",xaxt="n"
     ,ylab = "no. of cases", main = "confirmed cases in world")
points(wdate,fitted(wfit),col="red",pch=1)
axis.Date(1, at=seq(min(wdate),max(wdate),by=10), format="%d %b %y")
legend("topleft",c("Actual","Predicted"), col=c("blue","red"), lwd=2)
```

```{r pressure, echo=FALSE}
a = today+1; b = today+7
predict_date <- as.Date(a:b,origin="2020-01-20")
new <- data.frame(wdate = as.Date(a:b ,origin = "2020-01-22"))
preddate <- data.frame(wdate = as.Date(a:b ,origin = "2020-01-21"))
pred_wconfirmed <-predict.lm(wfit,new,interval = "confidence",level = 0.95)
newworld_df <- cbind(preddate, pred_wconfirmed)
names(newworld_df)[3] <- "minimum"
names(newworld_df)[4] <- "maximum"
names(newworld_df)[1] <- "date"
```

### Predictions for total confirmed cases in World for next week:

```{r echo=FALSE}
knitr::kable(newworld_df,align = "crrr",format.args = list(big.mark = ",", 
  scientific = FALSE))
```

```{r echo=FALSE}
errdate <- data.frame(date = as.Date(0:(today-101),origin = "2020-05-01"))
errfit <- predict.lm(lm(wconfirmed[101:today]~poly(wdate[101:today],6)),errdate)
errfit <- round(errfit)
actual <- wconfirmed[101:today]
#sse <- sum((errfit-actual)**2) # SSE
err <- cbind(errdate,errfit,actual)
err <- cbind(err,error = ape(actual,errfit)*100)
err$error <- round(err$error,2)
#error <- sqrt((errfit[1:(today-100)]-actual[1:(today-100)])**2)
#rmse <- data.frame(rmse = sqrt(mean((errfit[1:(today-100)]-actual[1:(today-100)])**2))) # RMSE
names(err)[2] <- "fit"
err$error <- paste(err$error,"%")
#rsq <- cor(err$fit, err$actual) ^ 2
```

### Graph showing total confirmed cases with our predictions for World:

```{r echo=FALSE}
par(las=2,mgp=c(5,1,0),mar=c(6,6,6,6))
plot(err$date,err$actual,pch = 16,xlab = "date", col = "blue",xaxt = "n"
     ,ylab = "no. of cases ", main = "confirmed cases in india")
points(err$date,err$fit,col="red",pch=1)
axis.Date(1, at=seq(min(err$date),max(err$date),by=1), format="%d %b %y")
legend("topleft",c("Actual","Predicted"), 
       col=c("blue","red"), lwd=2)
```

### Error Analysis:

```{r echo=FALSE}
knitr::kable(err,align = "crrr",format.args = list(big.mark = ",", 
  scientific = FALSE))
```
